---
title: "Report"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
#Read the dataset
library(readxl)
library(tidyverse)
library(factoextra)
library(corrplot)
library(foreign)
library(psych)
library(pander)
library(xtable)
library(xtable)
library(MASS)
library(knitr)
library(pscl)
library(stargazer)
license.df<-na.omit(read_xlsx("Data/upload_date.xlsx",1))
#Create the factors
factor.df<-na.omit(read.csv("Data\\AggreatedData3.csv"))
```

## Descriptive Statistics

The main dataset used has the follow Descriptive Statistics:

```{r, echo=FALSE, warning=FALSE, results="asis"}
table.desc <- describe(license.df[,7:21])
table.desc <- table.desc[,c(-1,-2,-13)]
colnames(table.desc)<-c("Mean","Standard Dev.", "Median", "Trimmed mean","Median Absolute Deviation","Min.","Max.","Range","Skewness","Kurtosis")
pandoc.table(table.desc, split.tables=Inf, style='rmarkdown')
```

The dataset contains `r length(unique(license.df$thing_author_id))` unique authors across `r min(license.df$upload_date)` and `r max(license.df$upload_date)` upload dates and a total of `r nrow(license.df)` observations. The next step was to find the factors based on the licenses using an agregatted dataset summarizing the variables by author and the Key periods (before 2012-09-24, between 2012-09-24 and 2013-11-05 and after 2013-11-05):

```{r,echo=FALSE, message=FALSE, warning=FALSE}
pca_rotated <- psych::principal(factor.df[,30:41], rotate="varimax", nfactors=4, scores=TRUE)

```

Then we used the sum scores by factor (DiStenfao, Zhu, and Mindrila, 2009) as follows: 

* **Factor 1:** copyleft = licence4 + licence10 + licence11 + licence12 + licence 9 

* **Factor 2:** anticompetition= licence3 +licence5 +licence7 (moral rights)

* **Factor 3:** anti_social_rivarly = licence2 + licence6 

* **Factor 4:** collective_rivalry = licence8 - licence1 (**Is this a minus sign???**)


```{r,echo=FALSE, message=FALSE, warning=FALSE}
factor.df$copyleft<-factor.df[,33]+factor.df[,39]+factor.df[,40]+factor.df[,38]+factor.df[,41]
factor.df$anticompetition<-factor.df[,32]+factor.df[,34]+factor.df[,36]
factor.df$anti_social_rivarly<-factor.df[,31]+factor.df[,35]
factor.df$collective_rivalry<-factor.df[,37]-factor.df[,30]
```

The correlation matrix between the liceses is given by:


```{r,echo=FALSE, message=FALSE, warning=FALSE}
cor.df<-round(cor(factor.df[,30:41]),4)
knitr::kable(cor.df, "html")
```

The correlation matrix including the factor is given by:

```{r,echo=FALSE, message=FALSE, warning=FALSE}
cor.df2<-round(cor(factor.df[,c(13,42:ncol(factor.df))]),4)
knitr::kable(cor.df2, "html")
```

## Main hypotheses:

The dependent variable: follow (in your data you labeled it as out)

The control variable: keyevents

The variables entered in the zero-inflated part are: made, and files count


```{r, message=FALSE, warning=FALSE}
factor.df$key.event<-as.factor(factor.df$key.event)
#Model 1:
m1 <- zeroinfl(out ~  key.event|made_count+ files_count, data = factor.df, dist = "negbin", EM = TRUE)
summary(m1)
save.image("Report1.RData")
```





The main predictors are: private-collective (which is dummy coded (for h1); and four types of license use (for h2); and the interaction effect between private-collective and collective rivalry

For H1 testing, the models to be tested in zinb are: 

Model 1: the zero inflated part by entering made and filescount
Model 2: the control variable – key events
Model 3 (for h1): the main predictors
Model 4 (for h2): the four types of license use
Model 5 (for h3): the interaction effect between private-collective and collective rivalry PLUS additional interaction effects between private-collecdtive with the other three licenses. 


h1: private-collective increases follow-on derivatives (in contrast to private, and free riding)


h2: The use of collective-rivalry license will increase follow-on derivatives (other license use will be included just to show collective-rivalry will result in significant follow-on derivatives)


h3: Collective-rivalry will positively moderate the relationship between private-collective and follow-on derivatives. 


for the h3 we need a decent plot. Last time, we are running out of time, this time we can't afford NOT to include the interaction plot. 



