---
title: "Statistical Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Revised model.

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE, results='asis'}
library(xtable)
library(MASS)
library(knitr)
library(pscl)
library(stargazer)
library(dplyr)
library(pastecs)
library(gmodels)
```

```{r, echo=TRUE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Read the dataset
license.df<-read.csv("Data/AggreatedData.csv")
license.df<-na.omit(license.df)
license.df$key.event<-as.factor(license.df$key.event)
license.df <- within(license.df, key.event <- relevel(key.event, ref = "1"))

#1. Rename ES to “license_choice” and then recode ES1 & ES3 as LC1 (label: no_derivative), ES2 as LC2 (attribution), ES4 as LC3 (antibusiness)
license.df <- license.df %>% 
                  mutate(LC1 = ES1+ES3,
                         LC2 = ES2,
                         LC3 = ES4) %>% 
                  select(-ES1,-ES2,-ES3,-ES4)


#2. Rename design_strategy as “appropriability_strategy” and recode blended strategy as “private-collective”, and the others remain the same. 
license.df <- license.df %>% 
              rename(appropriability_strategy = design.strategy)

levels(license.df$appropriability_strategy)[levels(license.df$appropriability_strategy)=="blended"] <- "private-collective"
```


#3. Test the relationship between appropriability strategy (AS) and license choice (LC)
##3a. First provide a table of descriptive statistics, and include a bivariate correlation table with all the variables used in the analysis, comment the relationship between appropriability strategy and license choice

###Descriptive statistics.
```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
options(scipen=100)
options(digits=2)
temp <- license.df %>% 
        select(-thing_author_id,-key.event,-appropriability_strategy)
tt<-stat.desc(temp)
kable(tt)
```

###Frequency Table between Key Event and Appropriability Strategy.
```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
CrossTable(license.df$key.event, license.df$appropriability_strategy)
```


###Bivariate correlation table with all the variables used in the analysis.
```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
res <- cor(temp)
kable(round(res, 4))
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
library(corrplot)
corrplot(res, type = "upper",  tl.col = "black", tl.srt = 45)
```

###Heterogeneous Correlation Matrix.
Correlation between qualitative and quantitative variables such as **appropriability strategy** and **license choice**:

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
library(polycor)
temp <- license.df %>% 
        mutate(LC1= ifelse(LC1>0,1,0),
               LC2 =ifelse(LC2>0,1,0),
               LC3=ifelse(LC3>0,1,0)) %>% 
        select(LC1,LC2,LC3, appropriability_strategy)
tt<-hetcor(temp)
tt
```


##3b. Use a multinomial logistic regression with license choice as the dependent variable and use appropriability strategy to predict the choice of license choice (this provides a validity check that private-collective  appropriability strategy is more likely to choose “attribution” (LC2), free-riding is more likely to choose antibusiness licenses (LC3), and private appropriability strategy is more likely to choose LC1. This provides testing of our first set of research hypotheses

I did not used the **multinomial logistic regression** because license choice it is not a multinomial variable anymore. We aggregated the data and counted the number of times that license choice was found by *thing_author_id* and *key.event*. Instead of that, I ran a Multivariate multiple regression:


```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
my.model <- lm(cbind(LC1,LC2,LC3) ~ appropriability_strategy+key.event+comments_count+collection_count+downloads_count+
                                    files_count+thing_like_count+made_count+remix_count+remixed_froms_count+
                                    views_count+tags_count,data=license.df) 
summary(my.model)
```

Manova results:

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
summary(manova(my.model))
```


#4. Use the zero inflated neg binomial (zinb) for modelling the effects on “out”. 
##4a. Model 1: the usual control variables (files count, likes, period and perhaps collection)

```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
library(pscl)
m1 <- zeroinfl(out ~ files_count+thing_like_count+collection_count+key.event | files_count+thing_like_count+collection_count, 
               data = license.df, dist = "negbin", EM = TRUE)
summary(m1)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
load("Chunk17.RData")
library(pscl)
library(stargazer)
summary(m1)
```

##4b. Model 2: the main effects of AS and LC: Private-collective  
```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Define the reference (Private-collective)
license.df <- within(license.df, appropriability_strategy <- relevel(appropriability_strategy, ref = "private-collective"))
m2 <- zeroinfl(out ~ files_count+thing_like_count+collection_count+key.event+appropriability_strategy+LC1+LC2+LC3
                 | files_count+thing_like_count+collection_count+appropriability_strategy+LC1+LC2+LC3, 
               data = license.df, dist = "negbin", EM = TRUE)
save.image("Chunk18.RData")
summary(m2)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
load("Chunk18.RData")
library(pscl)
library(stargazer)
summary(m2)
```

##4c. Model 3: testing the following two sets of interaction effects (H4, H5) 
Appropriability strategy x Period (or key events):
```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
m3 <- zeroinfl(out ~ files_count+thing_like_count+collection_count+key.event+appropriability_strategy+LC1+LC2+LC3+(appropriability_strategy*key.event)+(appropriability_strategy*key.event)
                 | files_count+thing_like_count+collection_count+appropriability_strategy+LC1+LC2+LC3, 
               data = license.df, dist = "negbin", EM = TRUE)
summary(m3)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
load("Chunk19.RData")
library(pscl)
library(stargazer)
summary(m3)
```

Note that by definition **Appropriability strategy = Design Strategy** so it does not make sense to test this interaction.

#Repeat the above steps with the outcome measure: “made”.
##4a. Model 1: the usual control variables (files count, likes, period and perhaps collection)

```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
library(pscl)
m1 <- zeroinfl(made_count ~ files_count+thing_like_count+collection_count+key.event | files_count+thing_like_count+collection_count, 
               data = license.df, dist = "negbin", EM = TRUE)
summary(m1)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
load("Chunk20.RData")
library(pscl)
library(stargazer)
summary(m1)
```

##4b. Model 2: the main effects of AS and LC: Private-collective  
```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
m2 <- zeroinfl(made_count ~ files_count+thing_like_count+collection_count+key.event+appropriability_strategy+LC1+LC2+LC3
                 | files_count+thing_like_count+collection_count+appropriability_strategy+LC1+LC2+LC3, 
               data = license.df, dist = "negbin", EM = TRUE)
summary(m2)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
load("Chunk21.RData")
library(pscl)
library(stargazer)
summary(m2)
```

##4c. Model 3: testing the following two sets of interaction effects (H4, H5) 
Appropriability strategy x Period (or key events):
```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
m3 <- zeroinfl(made_count ~ files_count+thing_like_count+collection_count+key.event+appropriability_strategy+LC1+LC2+LC3+(appropriability_strategy*key.event)+(appropriability_strategy*key.event)
                 | files_count+thing_like_count+collection_count+appropriability_strategy+LC1+LC2+LC3, 
               data = license.df, dist = "negbin", EM = TRUE)
summary(m3)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
load("Chunk22.RData")
library(pscl)
library(stargazer)
summary(m3)
```