---
title: "Statistical Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#George message 5.
##1. use free riding as our reference model or private riding as our reference model
*I suspect there won’t be any difference between free riding and private. If that’s the case, we will chose private as our reference*
###Standard negative binomial model.

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE, results='asis'}
library(xtable)
library(MASS)
library(knitr)
library(pscl)
library(stargazer)
```

```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Read the dataset
license.df<-read.csv("Data/AggreatedData.csv")
license.df<-na.omit(license.df)
license.df$key.event<-as.factor(license.df$key.event)
license.df <- within(license.df, key.event <- relevel(key.event, ref = "1"))

#Define the reference (free-riding)
license.df <- within(license.df, design.strategy <- relevel(design.strategy, ref = "free-riding"))

#Standard negative binomial model
library(MASS)
library(knitr)
m.full <- glm.nb(out ~(1+design.strategy+key.event)+
                      (files_count+ thing_like_count+collection_count)*(1+design.strategy+key.event), data = license.df)
res<-summary(m.full)
res
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE, results='asis'}
library(xtable)
load("Chunk6.RData")
table <- xtable(res)
# Coefficients
print(
   xtable(table, align="lcccc"), # align columns
   type = "html", 
   html.table.attributes = 'align="center", # center table in page
                            rules="rows",   # only keep horizontal rows
                            width=50%,      # increase table width to 50% page
                            frame="below"') # remove border except bottom rule
```

Using as **private** reference:

```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Define the reference (free-riding)
license.df <- within(license.df, design.strategy <- relevel(design.strategy, ref = "private"))

#Standard negative binomial model
library(MASS)
library(knitr)
m.full <- glm.nb(out ~(1+design.strategy+key.event)+
                      (files_count+ thing_like_count+collection_count)*(1+design.strategy+key.event), data = license.df)
res<-summary(m.full)
res
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE, results='asis'}
library(xtable)
load("Chunk7.RData")
table <- xtable(res)
# Coefficients
print(
   xtable(table, align="lcccc"), # align columns
   type = "html", 
   html.table.attributes = 'align="center", # center table in page
                            rules="rows",   # only keep horizontal rows
                            width=50%,      # increase table width to 50% page
                            frame="below"') # remove border except bottom rule
```


###Zero-inflated negative binomial model - Model 1.

```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Define the reference (free-riding)
license.df <- within(license.df, design.strategy <- relevel(design.strategy, ref = "free-riding"))

#Zero-inflated negative binomial model
library(pscl)
m1 <- zeroinfl(out ~ files_count+thing_like_count+collection_count+key.event | files_count+thing_like_count+collection_count+key.event , data = license.df,
               dist = "negbin", EM = TRUE)
summary(m1)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
load("Chunk8.RData")
library(pscl)
library(stargazer)
summary(m1)
```

The **vuong** test for this model is given by:

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
m2<- glm.nb(out ~ files_count+thing_like_count+collection_count+key.event, data = license.df)
vuong(m1, m2)
```

Using as **private** reference:

```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Define the reference (private)
license.df <- within(license.df, design.strategy <- relevel(design.strategy, ref = "private"))

#Zero-inflated negative binomial model
library(pscl)
m1 <- zeroinfl(out ~ files_count+thing_like_count+collection_count+key.event| files_count+thing_like_count+collection_count+key.event , data = license.df,
               dist = "negbin", EM = TRUE)
summary(m1)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
library(xtable)
load("Chunk9.RData")
summary(m1)
```

The **vuong** test for this model is given by:

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
m2<- glm.nb(out ~ files_count+thing_like_count+collection_count+key.event, data = license.df)
vuong(m1, m2)
```

###Zero-inflated negative binomial model - Model 2.

```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Define the reference (free-riding)
license.df <- within(license.df, design.strategy <- relevel(design.strategy, ref = "free-riding"))

#Zero-inflated negative binomial model
m1 <- zeroinfl(out ~ files_count+thing_like_count+collection_count+ design.strategy+
                     ES1+ES2+ES3+ES4 + key.event | files_count+thing_like_count+collection_count+ design.strategy+
                     ES1+ES2+ES3+ES4 + key.event , data = license.df,
               dist = "negbin", EM = TRUE)
summary(m1)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE,}
load("Chunk10.RData")
summary(m1)
```

The **vuong** test for this model is given by:

```{r, echo=FALSE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
m2<- glm.nb(out ~ files_count+thing_like_count+collection_count+ design.strategy+
                     ES1+ES2+ES3+ES4 + key.event , data = license.df)
vuong(m1, m2)
```

Using as **private** reference:

```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Define the reference (private)
license.df <- within(license.df, design.strategy <- relevel(design.strategy, ref = "private"))

#Zero-inflated negative binomial model
library(pscl)
m1 <- zeroinfl(out ~ files_count+thing_like_count+collection_count+ design.strategy+
                     ES1+ES2+ES3+ES4 + key.event | files_count+thing_like_count+collection_count+ design.strategy+
                     ES1+ES2+ES3+ES4 + key.event , data = license.df,
               dist = "negbin", EM = TRUE)
summary(m1)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
library(xtable)
load("Chunk11.RData")
tt<-summary(m1)
summary(m1)
```

The **vuong** test for this model is given by:

```{r, echo=FALSE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
m2<- glm.nb(out ~ files_count+thing_like_count+collection_count+ design.strategy+
                     ES1+ES2+ES3+ES4 + key.event , data = license.df)
vuong(m1, m2)
```





