---
title: "Statistical Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#George message 4.
Further to our discussion, below I’d try to summarise. 

In my prior analysis, I used zero-inflated negative binomial regression
1. dependent variables = out 
2. control variables = files_count, thing_like_count, collection_count
3. design strategy, period as the main effects, and their interactions

##Standard negative binomial model.
```{r, echo=TRUE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Read the dataset
license.df<-read.csv("Data/AggreatedData.csv")
license.df<-na.omit(license.df)
#Standard negative binomial model
library(MASS)
library(knitr)
m.full <- glm.nb(out ~(1+design.strategy+key.event)+
                      (files_count+ thing_like_count+collection_count)*(1+design.strategy+key.event), data = license.df)
res<-summary(m.full)
res
save.image("Chunk1.RData")
```


##Model 1.
In your analysis, you can include the following tests or models

1. Model 1 with all the control variables plus the period to account the zero part (re period, I am not sure whether this should be included in model 2)


```{r, echo=TRUE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Zero-inflated negative binomial model
library(pscl)
m1 <- zeroinfl(out ~ files_count+thing_like_count+collection_count| key.event , data = license.df,
               dist = "negbin", EM = TRUE)
summary(m1)
save.image("Chunk2.RData")
```


##Model 2.
2. Model 2 with all the controls plus the main effects (design strategy, ES)

```{r, echo=TRUE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Zero-inflated negative binomial model
m2 <- zeroinfl(out ~ files_count+thing_like_count+collection_count+ design.strategy+
                     ES1+ES2+ES3+ES4 | key.event , data = license.df,
               dist = "negbin", EM = TRUE)
summary(m2)
save.image("Chunk3.RData")
```



##Model 3.
3. Model 3 = model 2 plus the interaction effect between design strategy x ES

```{r, echo=TRUE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Zero-inflated negative binomial model
m3 <- zeroinfl(out ~ (1+files_count+thing_like_count+collection_count)*(1+design.strategy+
                     ES1+ES2+ES3+ES4) | key.event , control=zeroinfl.control(method = "BFGS", maxit = 100000), data = license.df,
               dist = "negbin", EM = TRUE)
summary(m3)
save.image("Chunk4.RData")
```

##Model 4.
In a separate analysis to explore archetypes of designers, can you use the changes of ES over the period to classify designers. 

1. can you inductively using some sort of reduction/cluster technique (using ES strategy to infer and cluster designers) 

```{r, echo=TRUE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Finite mixture of negative binomial regression  (FLXMRnegbin)
library(countreg)
library(flexmix)
mycont <- list(iter = 1000, tol = 0.1, class = "r")
as(mycont, "FLXcontrol")
fm0 <- flexmix(out ~ files_count+thing_like_count+collection_count, 
               data = license.df, k = 2, model = FLXMRnegbin(), control= mycont)
summary(fm0)
parameters(fm0)

#Plots
rf0 <- lapply(1:2, function(i)
  glm.nb(out ~ files_count+thing_like_count+collection_count, data = license.df, weights = posterior(fm0)[,i]))
save.image("Chunk5.RData")
## Rootograms
r01 <- rootogram(rf0[[1]])
r02 <- rootogram(rf0[[2]])

par(mfrow = c(1, 2))
rootogram(glm.nb(out ~ files_count+thing_like_count+collection_count, data = license.df))
plot(r01 + r02)

```








