---
title: "Statistical Analysis"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Revised model.

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE, results='asis'}
library(xtable)
library(MASS)
library(knitr)
library(pscl)
library(stargazer)
library(tidyverse)
library(pastecs)
library(gmodels)
```

```{r, echo=TRUE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Read the dataset
license.df<-read.csv("Data/AggreatedData.csv")
license.df<-na.omit(license.df)
license.df$key.event<-as.factor(license.df$key.event)
license.df <- within(license.df, key.event <- relevel(key.event, ref = "1"))

#1. Rename ES to “license_choice” and then recode ES1 & ES3 as LC1 (label: no_derivative), ES2 as LC2 (attribution), ES4 as LC3 (antibusiness)
license.df <- license.df %>% 
                  mutate(LC1 = ES1+ES3,
                         LC2 = ES2,
                         LC3 = ES4) %>% 
                  select(-ES1,-ES2,-ES3,-ES4)


#2. Rename design_strategy as “appropriability_strategy” and recode blended strategy as “private-collective”, and the others remain the same. 
license.df <- license.df %>% 
              rename(appropriability_strategy = design.strategy)

levels(license.df$appropriability_strategy)[levels(license.df$appropriability_strategy)=="blended"] <- "private-collective"
```



##2c. Remember to run the interaction effect between AS and period. Can you carry out some sort of 2-step model, model one includes all the control, and the main predictors, and model two adds the interaction effect. And then compare the significant changes between model one and model using R-squared change. 

Here the same Multivariate Regression Model with the AS and Key.period interaction


```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
license.df <- within(license.df, appropriability_strategy <- relevel(appropriability_strategy, ref = "private"))
library(broom)
my.model <- lm(cbind(LC1,LC2,LC3) ~ appropriability_strategy+key.event+collection_count+
                                    files_count+thing_like_count+made_count+(appropriability_strategy*key.event)
                                    ,data=license.df) 

coef<-tidy(my.model)
table1<-coef[,c(1,2,3)]
table1<- table1 %>%
         spread(response, estimate) 
colnames(table1)[1]<-"Coefficients"
kable(table1)

table2<-coef[,c(1,2,4)]
table2<- table2 %>%
         spread(response, std.error) 
colnames(table2)[1]<-"Std. Error"
kable(table2)

table3<-coef[,c(1,2,5)]
table3<- table3 %>%
         spread(response, statistic) 
colnames(table3)[1]<-"Z-value"
kable(table3)

table4<-coef[,c(1,2,6)]
table4<- table4 %>%
         spread(response, p.value) 
colnames(table4)[1]<-"P-value"
kable(table4)
```

The **LC1** model presents Multiple R-squared:  0.248 and	Adjusted R-squared:  0.248. The **LC2** model presents
Multiple R-squared:  0.541,	Adjusted R-squared:  0.54 and finally, the **LC3** model presents Multiple R-squared:  0.192,	Adjusted R-squared:  0.192.

The Manova results are:

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
summary(manova(my.model))
```


2d. because one of the research hypotheses is about private-collective is more likely to sustain contribution. it’ll be useful to plot the interaction effects (see the attached for an illustration of the interaction between LC and period)

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
temp<-license.df
temp$key.event<-as.numeric(temp$key.event)
temp$Date<-ifelse(temp$key.event==1,"[2008-10-19, 2012-09-24)",
                       ifelse(temp$key.event==2,"[2012-09-24, 2013-11-05)", "[2013-11-05, 2014-07-02)"))

Appropriability.Strategy<-temp$appropriability_strategy
interaction.plot(temp$key.event,Appropriability.Strategy,temp$LC1,
                 ylab="License choice 1",xaxt="n",xlab="")
axis(1, at=c(1, 2, 3), labels=c("2012-09-24", "2013-11-05", "2014-07-02"), tck=.01, cex.axis=0.9, srt=45, col.ticks = "grey", las=2)

Appropriability.Strategy<-temp$appropriability_strategy
interaction.plot(temp$key.event,Appropriability.Strategy,temp$LC2,
                 ylab="License choice 2",xaxt="n",xlab="")
axis(1, at=c(1, 2, 3), labels=c("2012-09-24", "2013-11-05", "2014-07-02"), tck=.01, cex.axis=0.9, srt=45, col.ticks = "grey", las=2)

Appropriability.Strategy<-temp$appropriability_strategy
interaction.plot(temp$key.event,Appropriability.Strategy,temp$LC3,
                 ylab="License choice 3",xaxt="n",xlab="")
axis(1, at=c(1, 2, 3), labels=c("2012-09-24", "2013-11-05", "2014-07-02"), tck=.01, cex.axis=0.9, srt=45, col.ticks = "grey", las=2)


```


#4. Use the zero inflated neg binomial (zinb) for modelling the effects on “out”. 
##4a. Model 1: the usual control variables (files count, likes, period and perhaps collection)

```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
library(pscl)
m1 <- zeroinfl(out ~ files_count+thing_like_count+collection_count+key.event | files_count+thing_like_count+collection_count, 
               data = license.df, dist = "negbin", EM = TRUE)
summary(m1)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
load("Chunk23.RData")
library(pscl)
library(stargazer)
summary(m1)
```


##4b. Model 2: the main effects of AS and LC: Private-collective  
```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Define the reference (Private-collective)
license.df <- within(license.df, appropriability_strategy <- relevel(appropriability_strategy, ref = "private"))
m2 <- zeroinfl(out ~ files_count+thing_like_count+collection_count+key.event+appropriability_strategy+LC1+LC2+LC3
                 | files_count+thing_like_count+collection_count+appropriability_strategy+LC1+LC2+LC3, 
               data = license.df, dist = "negbin", EM = TRUE)
save.image("Chunk24.RData")
summary(m2)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
load("Chunk24.RData")
library(pscl)
library(stargazer)
summary(m2)
```


##4c. Model 3: testing the following two sets of interaction effects (H4, H5) 
Appropriability strategy x Period (or key events):
```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
m3 <- zeroinfl(out ~ files_count+thing_like_count+collection_count+key.event+appropriability_strategy+LC1+LC2+LC3+(appropriability_strategy*key.event)
                 | files_count+thing_like_count+collection_count+appropriability_strategy+LC1+LC2+LC3+(appropriability_strategy*key.event), 
               data = license.df, dist = "negbin", EM = TRUE)
summary(m3)
save.image("Chunk25.RData")
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
load("Chunk25.RData")
library(pscl)
library(stargazer)
summary(m3)
```

Note that by definition **Appropriability strategy = Design Strategy** so it does not make sense to test this interaction.

#Repeat the above steps with the outcome measure: “made”.
##4a. Model 1: the usual control variables (files count, likes, period and perhaps collection)

```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
library(pscl)
m1 <- zeroinfl(made_count ~ files_count+thing_like_count+collection_count+key.event | files_count+thing_like_count+collection_count, 
               data = license.df, dist = "negbin", EM = TRUE)
summary(m1)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
load("Chunk26.RData")
library(pscl)
library(stargazer)
summary(m1)
```

##4b. Model 2: the main effects of AS and LC: Private-collective  
```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
m2 <- zeroinfl(made_count ~ files_count+thing_like_count+collection_count+key.event+appropriability_strategy+LC1+LC2+LC3
                 | files_count+thing_like_count+collection_count+appropriability_strategy+LC1+LC2+LC3, 
               data = license.df, dist = "negbin", EM = TRUE)
summary(m2)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
load("Chunk27.RData")
library(pscl)
library(stargazer)
summary(m2)
```


##4c. Model 3: testing the following two sets of interaction effects (H4, H5) 
Appropriability strategy x Period (or key events):
```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
m3 <- zeroinfl(made_count ~ files_count+thing_like_count+collection_count+key.event+appropriability_strategy+LC1+LC2+LC3+(appropriability_strategy*key.event)
                 | files_count+thing_like_count+collection_count+appropriability_strategy+LC1+LC2+LC3+(appropriability_strategy*key.event), 
               data = license.df, dist = "negbin", EM = TRUE)
summary(m3)
```

```{r, echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
load("Chunk28.RData")
library(pscl)
library(stargazer)
summary(m3)
```

