---
title: "Statistical Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#George message 3.
##Can you use individual designer as our unit of analysis.
That's, by collating and aggregating contribution of each designer, our unit of analysis becomes the designer's design portfolio. 

```{r, echo=TRUE,eval=TRUE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Call the library
library(readxl)
#Read the dataset
license.df<-read_xlsx("Data/upload_date.xlsx",1)
#Create the factors
license.df$license<-as.factor(license.df$license)
license.df$Type <-as.factor(license.df$Type )
```


Somehow we need to retain the time information considering the key events that may affect designer's contribution. For example, when Makerbot decided to make hardware closed source (see the attached Makerbot Timeline for other events). One of the caveats is that the data will become too sparse as some contributors may not consistently contribute over time. This will result in an unbalanced panel. But give and take, we need to account for two key incidents:  event number 4 (happened in 24.09.2012), and number 8 (05.11.2013). We use these two time points to temporally divide our data into three periods: prior to closed source will be the first period, followed by the period after closed source announcement, until patent infringement and from that onwards our third period.


```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Invoke dplyr package
library(tidyverse)
license.df<-license.df %>% 
  mutate(key.event=ifelse(upload_date<"2012-09-24","1",
                   ifelse(upload_date<"2013-11-05","2","3")))
```


##Summarize data based on thing_author_id,key.event.

```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Summarize by sum
summa1.df<-license.df %>% 
           group_by(thing_author_id,key.event) %>% 
           summarise(comments_count=sum(comments_count),
                     collection_count=sum(collection_count),
                     downloads_count=sum(downloads_count),
                     files_count=sum(files_count),
                     thing_like_count=sum(thing_like_count),
                     made_count=sum(made_count),
                     remix_count=sum(remix_count),
                     remixed_froms_count=sum(remixed_froms_count),
                     views_count=sum(views_count),
                     out=sum(out),
                     tags_count=sum(tags_count)
                     )
```


##Create categories
Create a category of design strategy based on the "in" column. First, if the in column is larger than 0 (i.e. in >0), then it means the design is NOT an original design, and is a derivative of prior design. 

Followed from this, if the in column = 0 (i.e. in = 0), then the design is original.  


We can use these two pieces of information to construct three types of design strategy: free riding (where there are zero counts of in=0 but non-zero counts of in>0); 

private (non-zero counts of in=0 but zero counts of in > 0), and blended (non-zero counts of  in>0 &  of in=0).

For example, a designer contributed 10 designs, say 5 designs with in>0, and the other 5 with in=0. Then, this designer is using a blended design strategy. 

The second designer shared 20 designs, however, all of her designs are derived from others' designers work (i.e. non-zero counts of n>0  but zero counts of n=0). This designer is using a free-riding (or mesh-up) design strategy.


Lastly, the third designer is using a private strategy when there are zero counts of in>0, but non-zero counts of in=0).  


```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Create the counts
temp <- license.df %>% 
             group_by(thing_author_id,key.event) %>% 
              summarize(n_conut = n(),
              larger  = sum(inv > 0),
              zero = sum(inv == 0))
#Classify
temp <- temp %>% 
        mutate(design.strategy=ifelse(larger>0 & zero>0,"blended",
                      ifelse(larger>0 & zero==0, "free-riding","private"))) %>% 
        select(-n_conut,-larger,-zero)
#Convert to factor
temp$design.strategy<-as.factor(temp$design.strategy)   

#Join with the license.df
results.df <- full_join(summa1.df, temp, by=c("thing_author_id","key.event"))
              
```


We use the licence types to identify several types of entrepreneurial strategy (ES): 

a. designs are shared under the most restrictive licences to mitigate business rivalry. So this includes any licences that discouraged commercial activities. The two main licences are "All Rights Reserved", "Attribution - Non-Commercial - No Derivatives", and "Creative Commons - Attribution - Non-Commercial); 

b. the use of the least restrictive licences to induce contributions from business and social actors. They are: "BSD License", "Creative Commons - Attribution", "Creative Commons- Attribution - Shake Alike";

c. the third type of ES is to mitigate social rivalry. The licenses are: "Creative Commons - Attribution - No Derivatives"; 
 
d. the final fourth type is anti-business. They are: "Creative Commons - Public Domain Dedication", "GNU - GPL", "GNU - LGPL", and "Public Domain".

```{r, echo=TRUE,eval=FALSE,message=FALSE,warning=FALSE, message=FALSE, warning=FALSE}
#Classify
license.df <- license.df %>% 
               mutate(entrepreneurial.strategy=
                        ifelse(license %in% c("All Rights Reserved",   "Attribution - Non-Commercial - No Derivatives","Attribution - Non-Commercial - Share Alike","Creative Commons - Attribution - Non-Commercial"),"1",   ifelse(license %in% c("BSD License", "Creative Commons - Attribution", "Creative Commons - Attribution - Share Alike"),"2",
                        ifelse(license %in% c("Creative Commons - Attribution - No Derivatives"),"3","4"))))

#Summarize by frequency
summa2.df<-license.df %>% 
           group_by(thing_author_id,key.event, entrepreneurial.strategy) %>% 
           summarise (freq = n()) 
#Spread
summa3.df<-summa2.df %>% 
           group_by(thing_author_id,key.event) %>% 
           spread(entrepreneurial.strategy,freq)

#Replace missing by zero
summa3.df[is.na(summa3.df)] <- 0
colnames(summa3.df)[3:6]<-c("ES1","ES2","ES3","ES4")

#Join all data
results.df <- full_join(results.df, summa3.df, by=c("thing_author_id","key.event"))
#sort data
results2.df<- results.df %>% 
             ungroup() %>%
             arrange(thing_author_id, key.event)
#Export data
write.csv(results2.df, "Data/AggreatedData.csv",  row.names = F)
```


At this stage, I'd run an inductive analysis by examining the relationship between the four ES types and our dependent measures (out, and made_count) to fine tune my prediction.


So we need to discuss this when you come to this point in time. Consider the high likelihood that license types may be subject to the two critical events (see point 2 re close source and patent). 


